Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
new abstract

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with object-based segmentation at larger timescales. Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates its potential, consistently outperforming baseline mel-frequency cepstral coefficients (MFCCs).

Representing the scene at larger time scale as a set of examplars of coherent segments is an effective approach for scene similarity retrieval as it allows the retrieval system to focus on discriminative features. This benefit is reduced in the supervised scene classification, probably because much of the discriminability potential of the approach is already learned by the classifier. \ja{This last part is very vague and hard for me to understand. Why is this the case?}
\end{abstract}

>>>>

This paper introduces a generic hierarchical modeling scheme for acoustic scenes using the wavelet scattering transform at sub-second timescales with object-based segmentation at larger timescales. Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets using a state-of-the-art classifier demonstrates the potential of featurs designed using the wavelet scattering transform, consistently outperforming baseline mel-frequency cepstral coefficients (MFCCs).

Also, representing the scene at larger time scale as a set of representative features of coherent segments is an effective approach for scene similarity retrieval as it allows the retrieval system to focus on discriminative features. 
\end{abstract}
